---
date: "`r format(Sys.Date())`"
title: "First contact with the data on R"
author: "Etienne Bacher"
draft: true
tags: ["R", "Stata"]
output: 
  blogdown::html_page:
    toc: false
---

In this post, you will see how to import and treat data, make descriptive statistics and a few plots. However, I am still a recent user of R and I don't know much about the optimal organization of files in a project (and many people explain it better than me online). Therefore, I will show you a personal method that is perhaps not the most effective but that works.

# Files used and organization of the project

<!-- BESOIN DE TROUVER LES BASES ORIGINALES SUR LE SITE DE LA BANQUE MONDIALE -->
The datasets that we will use come from........

In the folder that contains the project, I have several sub-folders: Figures, Bases_Used, Bases_Created. To be able to save or use files in these particular sub-folders, I put their path as vectors.

```{r}
figdir <- c("/your/path/to/your/project/Figures/")
base_used_dir <- c("/your/path/to/your/project/Bases_Used/")
base_created_dir <- c("/your/path/to/your/project/Bases_Created/")
```


# Import data

We will use data contained in Excel (`.xlsx`) and text (`.txt`) files. To import Excel data, we wil need the `readxl` package. 

```{r}
# if you've never installed this package before, do:
# install.packages("readxl")
library(readxl)
```


